---
title: "02 - Tables for maps"
author: "Yann Say"
date: last-modified
---

```{r setup, message=FALSE}
library(presentresults)
library(dplyr)
results_table <- expand.grid(analysis_var = c("msni_in_need", "comp_health_in_need", "comp_prot_in_need", "comp_edu_in_need", "comp_foodsec_in_need","comp_wash_in_need",        "comp_snfi_in_need"),
                             analysis_var_value = c(1,0),
                             group_var = "admin1",
                             group_var_value = c("PCODE1", "PCODE2"))

set.seed(12344)
results_table$stat <-runif(nrow(results_table))
```

This vignette will show an example of how to create a table for the MSNA Indicator Maps 1.2 tool.

## `create_table_for_map`

La tabla de resultados (generada aleatoriamente) que se muestra a continuación presenta los resultados en formato largo para 7 indicadores y a nivel administrativo 1:

- **msni_in_need**: Puntaje del Índice de Necesidades Multisectoriales  
- **comp_health_in_need**: Puntaje compuesto sectorial de Salud  
- **comp_prot_in_need**: Puntaje compuesto sectorial de Protección  
- **comp_edu_in_need**: Puntaje compuesto sectorial de Educación  
- **comp_foodsec_in_need**: Puntaje compuesto sectorial de Seguridad Alimentaria  
- **comp_wash_in_need**: Puntaje compuesto sectorial de Agua, Saneamiento e Higiene  
- **comp_snfi_in_need**: Puntaje compuesto sectorial de Refugio y Artículos No Alimentarios  
- **admin1**: **PCODE1** y **PCODE2**.  

La columna **stat** representa los porcentajes.

```{r}
head(results_table)
```

Maps can only show one information per admin level. First thing is to filter the results table for the information to get the information to be map. In the example, the analysis variable value can be 1 or 0, where 1 means "in need", and 0 means "not in need". The map will show the percentages of household in needs, the results will be filtered for 1. Then the function `create_table_for_map` can be used.

```{r}
results_table_filtered <- results_table |> 
  filter(analysis_var_value == "1")

results_table_recoded_5_classes <- results_table_filtered %>% 
  create_table_for_map(number_classes = 5)

results_table_recoded_5_classes
```

If you want to use 6 classes, set the argument `number_classes` to 6.

```{r}
results_table_filtered %>% 
  create_table_for_map(number_classes = 6)
```


There can be 5 or 6 classes as follow:

:::: {.columns}

::: {.column width="45%"}
### 5 classes

| Class | Value         |
|-------|---------------|
| 1     | 0             |
| 2     | \<= 25%       |
| 3     | \<= 50%       |
| 4     | \<= 75%       |
| 5     | \<= 100%      |
| empty | Anything else |
:::

::: {.column width="10%"}
<!-- empty column to create gap -->
:::

::: {.column width="45%"}
### 6 classes

| Class | Value         |
|-------|---------------|
| 1     | 0             |
| 2     | \<= 20%       |
| 3     | \<= 40%       |
| 4     | \<= 60%       |
| 5     | \<= 80%       |
| 6     | \<= 100%      |
| empty | Anything else |
:::

::::

## Troubleshooting

If you have more than one value per indicator and admin level, you should get a warning from tidyr. You can use it to explore where the problem lies.

```{r}
results_table %>% 
  create_table_for_map()
```
```{r}
results_table |>
  dplyr::summarise(n = dplyr::n(), .by = c(group_var_value, analysis_var)) |>
  dplyr::filter(n > 1L)
```

In this case there are 2 values for each combination of *group_var_value* and *analysis_var*.

```{r}
results_table |>
  filter(group_var_value == "PCODE1" & analysis_var == "msni_in_need")
```
There are two values, maps can only show one. The results table should be filtered to one value only.

This is section comes from this [vignette](https://impact-initiatives.github.io/presentresults/articles/create-table-for-map.html). 
