---
title: "04 - Practice (8)"
author: "Yann Say"
date: last-modified
---
# Practice

## Practice 1

- Add IMPACT theme to the following barplot `initialplot`

```{r}
#| message: false
library(presentresults)
library(dplyr)

data_to_plot <- presentresults::presentresults_MSNA2024_labelled_results_table |>
  dplyr::filter(
    analysis_var == "wash_sanitation_facility_cat",
    group_var == "admin1") |> 
  dplyr::mutate(label_analysis_var_value = factor(label_analysis_var_value,
                                                  levels = c("Improved",
                                                             "Unimproved",
                                                             "None",
                                                             "Undefined")))
initialplot <- data_to_plot %>%
  ggplot2::ggplot() +
  ggplot2::geom_col(
    ggplot2::aes(
      x = label_analysis_var_value,
      y = stat,
      fill = label_group_var_value
    ),
    position = "dodge"
  ) +
  ggplot2::labs(
    title = stringr::str_wrap(unique(data_to_plot$indicator), 50),
    x = stringr::str_wrap(unique(data_to_plot$label_analysis_var), 50),
    fill = stringr::str_wrap(unique(data_to_plot$label_group_var), 20)
  )

initialplot
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the argument *palette* in `theme_barplot`?
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Have you looked at the object `impact_palettes`?
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the argument *initiative* in `theme_impact`?
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
initialplot + 
  theme_barplot(palette = impact_palettes$impact_palette) +
  theme_impact("impact")
```
:::

## Practice 2

- You have the following results table. You want to create a map that shows the percentages of households using surface water (`surface_water`, **Surface water**) as main drinking water source (`wash_drinking_water_source_cat`, **Category of the drinking water source**) per admin level 1 (`admin1`, **Admin 1**). 

- Create the table that should be share to the GIS team, the table should have 5 classes (0, less than 20%, less than 40%, less than 60%, less than 80% and less than 100%).

```{r}
library(presentresults)
library(dplyr)
data_to_map <- presentresults::presentresults_MSNA2024_labelled_results_table
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you filter `data_to_map` for only *surface_water* in *wash_drinking_water_source_cat*?
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you filter `data_to_map` for only *admin1*?
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer
```{r}
data_filtered <- data_to_map |> 
  filter(
        analysis_var == "wash_drinking_water_source_cat",
        analysis_var_value == "surface_water",
        group_var == "admin1"
)
results_table_recoded_5_classes <- data_filtered |> 
  create_table_for_map(number_classes = 5)

results_table_recoded_5_classes
```
:::

## Practice 3

- Try the tabular html output. 
- Try to edit the authors, RCID and the introduction.
