---
title: "04 - Practice (8)"
author: "Yann Say"
date: last-modified
---
# Ejercicio

## Ejercicio 1

- Add IMPACT theme to the following barplot `initialplot`

```{r}
data_to_plot <- presentresults::presentresults_MSNA2024_labelled_results_table |>
  dplyr::filter(
    analysis_var == "wash_sanitation_facility_cat",
    group_var == "admin1") |> 
  dplyr::mutate(label_analysis_var_value = factor(label_analysis_var_value,
                                                  levels = c("Improved",
                                                             "Unimproved",
                                                             "None",
                                                             "Undefined")))
initialplot <- data_to_plot %>%
  ggplot2::ggplot() +
  ggplot2::geom_col(
    ggplot2::aes(
      x = label_analysis_var_value,
      y = stat,
      fill = label_group_var_value
    ),
    position = "dodge"
  ) +
  ggplot2::labs(
    title = stringr::str_wrap(unique(data_to_plot$indicator), 50),
    x = stringr::str_wrap(unique(data_to_plot$label_analysis_var), 50),
    fill = stringr::str_wrap(unique(data_to_plot$label_group_var), 20)
  )
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the argument *palette* in `theme_barplot`?
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Have you looked at the object `impact_palettes`?
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the argument *initiative* in `theme_impact`?
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
initialplot + 
  theme_barplot(palette = impact_palettes$impact_palette) +
  theme_impact("impact")
```
:::

## Ejercicio 2

- tablas para la mapas

## Ejercicio 3

- Pruebe el resultado en formato HTML tabular.
- Intente editar los autores, RCID y la introducción.

