---
title: "03 - Practice (5)"
author: "Yann Say"
date: last-modified

---
# Practices

## Practice 1

```{r}
#| message: false
library(analysistools)
library(dplyr)

my_data <- analysistools::analysistools_MSNA_template_data

sampling_frame <- data.frame(
  strata = c("admin1a", "admin1b", "admin1c"),
  population = c(100000, 200000, 300000)
)
```

Create the analysis for the following indicators:

- % of households having/had soap at home 
- % of households by type of primary source of drinking water 
- % of households by self-reported barriers to accessing health care	
- Average household income over the 30 days prior to data collection (total)
- Median household income over the 30 days prior to data collection (total)
- Average household expenditures in the 6 months prior to data collection (health)
- Median household expenditures in the 6 months prior to data collection (health)
- Ratio household expenditures on health in the 6 months prior to data collection and the household income over the 30 days prior to data collection.
- % of households per number of days when the household had to restrict consumption by adults in order for small children to eat to cope with a lack of food or money to buy it.

The analysis should be at **admin1** level (the strata). 

```{r}
#| echo: false
analysistools_MSNA_template_survey %>% 
  filter(name %in% c("wash_soap", "wash_drinkingwatersource", "health_barriers", "income_v2_total", "expenditure_health", "rCSIMealAdult")) %>% 
  select(name, `label::english`, type) %>% 
  mutate(`label::english` = case_when(`label::english` == "${health_barriers_question_select}" ~ "What are your barriers to access health care?", 
                                      TRUE ~ `label::english`))
```
```{r}
exercise_data <- analysistools::analysistools_MSNA_template_data

exercise_sampling_frame <- data.frame(
  strata = c("admin1a", "admin1b", "admin1c"),
  population = c(100000, 200000, 300000)
)

template_loa <- readxl::read_excel("../inputs/08 - exercise - template loa.xlsx")
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

*rCSIMealAdult* should be analysed as a categorical variable not a numerical variable to get the proportion per day.

:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
exercise_data <- exercise_data %>%
  add_weights(
    exercise_sampling_frame,
    "admin1", "strata", "population"
  )

exercise_design <- srvyr::as_survey_design(exercise_data, weights = "weights", strata = "admin1")

exercise_loa <- readxl::read_excel("../inputs/09 - correction - loa.xlsx")

exercise_results <- create_analysis(exercise_design, loa = exercise_loa, sm_separator = "/")

```

:::

## Downloads

- [08 - exercise - template loa](../inputs/08 - exercise - template loa.xlsx)
- [09 - correction - loa](../inputs/09 - correction - loa.xlsx)
