---
title: "01 - List of analysis"
author: "Yann Say"
date: last-modified

---
```{r}
#| warning: false
library(analysistools)
library(dplyr)

my_data <- analysistools::analysistools_MSNA_template_data

sampling_frame <- data.frame(
  strata = c("admin1a", "admin1b", "admin1c"),
  population = c(100000, 200000, 300000)
)

set.seed(1323)
my_data <- my_data |>
  mutate(num_aged_school_children = round(runif(100, min = 0, max = 5)),
         num_enrolled_school_children = round(runif(100, min = 0, max = 5)),
         num_enrolled_school_children = case_when(num_aged_school_children == 0 ~ NA, num_aged_school_children < num_enrolled_school_children ~ num_aged_school_children,
                                                  TRUE ~ num_enrolled_school_children
                                                  ))
```

# Analysis - list of analysis

## `create_analysis` and list of analysis (loa)

List of analysis (loa) is a list with all analysis to be performed. It takes the form of a data frame with minimum 4 columns:

- *analysis_type* : The analysis type that should be performed.
- *analysis_var* : The analysis variable or dependent variable.
- *group_var* : The grouping variable or independent variable.
- *level* : The confidence level (expressed between 0 and 1).

```{r}
my_loa <- analysistools::analysistools_MSNA_template_loa

my_loa
```

The loa can be passed as argument to the `create_analysis` function. 

```{r}
#| output: false
my_data <- my_data %>% 
  add_weights(sampling_frame, "admin1", "strata", "population")

my_design <- srvyr::as_survey_design(my_data, weights = "weights", strata = "admin1")
my_results <- create_analysis(my_design, loa = my_loa, sm_separator = "/")
```

The calculations are made only for the indicators in the loa. That way the analysis can be tailored to specific needs.
```{r}
head_results_table <- my_results$results_table %>% 
  head(5)

tail_results_table <- my_results$results_table %>% 
  tail(5)

rbind(head_results_table,tail_results_table)
```
