---
title: "04 - Practice - session 1"
author: "Yann Say"
date: last-modified

---
# Practice

## Practice 1

Try the following with a dataset:

-   Perform a check to spot personal identifiable information

```{r}
library(cleaningtools)
library(dplyr)

my_raw_dataset <- cleaningtools::cleaningtools_raw_data
my_kobo_survey <- cleaningtools::cleaningtools_survey
my_kobo_choice <- cleaningtools::cleaningtools_choices
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Try the function `check_pii`
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
my_raw_dataset %>% 
  check_pii(uuid_column = "X_uuid")
```
:::

## Practice 2

-   Perform a check that will look at the percentages of missing value per observation and that will spot any observation that is *different*.

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Try the function `check_percentage_missing`
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try to add a new column with `add_percentage_missing`
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
my_data_with_missing <- my_raw_dataset %>% 
  add_percentage_missing(kobo_survey = my_kobo_survey)
  
my_data_with_missing %>% 
  check_percentage_missing(uuid_column = "X_uuid")
```

Or if using a log already

```{r}
#| output: false
a_log <- my_raw_dataset %>% 
  check_pii(uuid_column = "X_uuid")
a_log$checked_dataset <- a_log$checked_dataset %>% 
  add_percentage_missing(kobo_survey = my_kobo_survey)
a_log %>% 
  check_percentage_missing(uuid_column = "X_uuid")
```
:::

## Practice 3

-   Fill the excel checklist to do the following checks:
    -   household number (variable: **num_hh_member**) is above 8.
    -   the water source for drinking water is bottled (variable: **water_source_drinking**, value: **bottled**) and the household always treat the drinking water (variable: **treat_drink_water**, value: **always_treat**).
    -   the water source for drinking water is bottled (variable: **water_source_drinking**, value: **bottled**) and one of the main reason for the the household to not meet its water needs is the water pressure (variable: **access_water_enough_why_not**, value: **water_pressure**, this is a select multiple)
    
```{r}
#| echo: false
my_kobo_survey %>% 
  filter(name %in% c("num_hh_member", "water_source_drinking", "treat_drink_water","access_water_enough_why_not")) %>% 
  select(name, `label::English (en)`, type)
  
my_kobo_choice %>% 
  filter(list_name %in% c("water_sources","treat", "barriers_water_needs"),
         name %in% c("bottled", "always_treat", "water_pressure")) %>% 
  select(name,`label::English (en)`, list_name )
```

```{r}
#| output: false
exercise_check_list <- readxl::read_excel("../inputs/01 - example - check_list.xlsx")

my_raw_dataset %>% 
    check_logical_with_list(uuid_column = "X_uuid",
                          list_of_check = exercise_check_list,
                          check_id_column = "check_id",
                          check_to_perform_column = "check_to_perform",
                          columns_to_clean_column = "columns_to_clean",
                          description_column = "description")
```

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
my_check_list <- data.frame(check_id = c("check_household number", "check_water_treatment", "check_3"),
                            description = c("num_hh_member is big","using bottled water and always treat","using bottled water and main reason is water pressure"),
                            check_to_perform = c("num_hh_member > 8","water_source_drinking == \"bottled\" & treat_drink_water == \"always_treat\"","water_source_drinking == \"bottled\" & access_water_enough_why_not.water_pressure == TRUE"),
                            columns_to_clean = c("num_hh_member","water_source_drinking, treat_drink_water","water_source_drinking, access_water_enough_why_not.water_pressure"))

my_raw_dataset %>% 
    check_logical_with_list(uuid_column = "X_uuid",
                          list_of_check = my_check_list,
                          check_id_column = "check_id",
                          check_to_perform_column = "check_to_perform",
                          columns_to_clean_column = "columns_to_clean",
                          description_column = "description")
```
:::

## Extra

-   Try to add duration with audit files.

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a tip

Try `create_audit_list()` and `add_duration_from_audit()`
:::

## Downloads

- [01 - example - check_list](../inputs/01 - example - check_list.xlsx)
