---
title: "03 - Checks with logical list"
author: "Yann Say"
date: last-modified

---
```{r}
#| warning: false
library(cleaningtools)
library(dplyr)

my_raw_dataset <- cleaningtools::cleaningtools_raw_data
my_kobo_survey <- cleaningtools::cleaningtools_survey
my_kobo_choice <- cleaningtools::cleaningtools_choices
```

## check_logical_with_list

In other cases, the check is specific and should be tailored to the dataset, for example, `check_logical_with_list`. All the logical checks can be recorded in an excel file.

```{r}
logical_check_list <- readxl::read_excel("../inputs/01 - example - check_list.xlsx")
logical_check_list
```

The check list has 4 columns:

-   check_id : the name of the check
-   description: the description of the check
-   check_to_perform: the check to perform. The format for the check to be performed should take the format based on tidyverse. That format is as if a new indicator is create with a mutate. That new indicator should be a logical (i.e. TRUE or FALSE) with TRUE being the value to flag.
-   columns_to_clean: the list of column names that are used for the logical check.

This list can then be used with `check_logical_with_list`.

```{r}
example_logic <- my_raw_dataset %>% 
  check_logical_with_list(uuid_column = "X_uuid",
                          list_of_check = logical_check_list,
                          check_id_column = "check_id",
                          check_to_perform_column = "check_to_perform",
                          columns_to_clean_column = "columns_to_clean",
                          description_column = "description")
```

```{r}

example_logic$logical_all %>% 
  head()
```

The log returns :

-   uuid
-   question: for all variables in **columns_to_clean**
-   old value: for all variables in **columns_to_clean**
-   issue
-   check_id: logical check identifier
-   check_binding: the combination of the check_id and the uuid.

One check can be flagged in several rows, in the example above, for each uuid, the primary_livelihood and tot_expenses are flagged.

Format for the **check_to_perform** should take the format based on *tidyverse*. That format is as if a new indicator is create with a `mutate`. That new indicator should be a logical (i.e. TRUE or FALSE) with TRUE being the value to flag.

```{r}
my_raw_dataset %>% 
  dplyr::mutate(xxx =  primary_livelihood.employment == 1 & tot_expenses < 200000) %>% 
  dplyr::select(X_uuid, xxx, primary_livelihood.employment, tot_expenses) %>% 
  head()
```

The checked dataset will be return with extra columns, i.e. a logical variable with the name of the **check_id**.

```{r}
example_logic$checked_dataset[1:6,tail(names(example_logic$checked_dataset))]
```

::: {.callout-note .column-margin}
If you don't include **columns_to_clean** the `check_logical_with_list` function will try to guess the variables. Not guarantee it will read or pick the correct names.
:::

## Downloads

- [01 - example - check_list](../inputs/01 - example - check_list.xlsx)
