---
title: "03 - Practice (3)"
author: "Yann Say"
date: last-modified

---
# Practice 

```{r}
#| message: false
library(impactR4PHU)
library(addindicators)
library(dplyr)
```

## Practice 1

- Add the **food consumption matrix score** to the dataset. The food consumption matrix score is a food security indicator that uses the **food consumption score**, **household hunger score** and the **reduced coping strategy index**.

```{r}
#| echo: false
names_to_keep <- grep("rCSI", analysistools::analysistools_MSNA_template_survey$name, value = T)
analysistools::analysistools_MSNA_template_survey %>% 
  filter(name %in% names_to_keep,
         name != "rCSI_module") %>% 
  select(name, `label::english`, type) 
```

```{r}
#| eval: false
library(impactR4PHU)
library(addindicators)
library(dplyr)
```

```{r}
exercise_data <- addindicators::addindicators_MSNA_template_data %>%
  add_fcs(
  cutoffs = "normal",
  fsl_fcs_cereal = "fs_fcs_cereals_grains_roots_tubers",
  fsl_fcs_legumes = "fs_fcs_beans_nuts",
  fsl_fcs_veg = "fs_fcs_vegetables_leaves",
  fsl_fcs_fruit = "fs_fcs_fruit",
  fsl_fcs_meat = "fs_fcs_meat_fish_eggs",
  fsl_fcs_dairy = "fs_fcs_dairy",
  fsl_fcs_sugar = "fs_fcs_sugar",
  fsl_fcs_oil = "fs_fcs_oil_fat_butter"
  ) %>%
  add_hhs(
  fsl_hhs_nofoodhh = "fs_hhs_nofood_yn",
  fsl_hhs_nofoodhh_freq = "fs_hhs_nofood_freq",
  fsl_hhs_sleephungry = "fs_hhs_sleephungry_yn",
  fsl_hhs_sleephungry_freq = "fs_hhs_sleephungry_freq",
  fsl_hhs_alldaynight = "fs_hhs_daynoteating_yn",
  fsl_hhs_alldaynight_freq = "fs_hhs_daynoteating_freq",
  yes_answer = "yes",
  no_answer = "no",
  rarely_answer = "rarely_1_2",
  sometimes_answer = "sometimes_3_10",
  often_answer = "often_10_times"
  )
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the function `add_fcm_phase`?
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

The food consumption matrix needs 3 indicators, FCS, rCSI, HHS.
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Have you used the correct HHS category variable?
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
my_answer <- exercise_data %>% 
  add_rcsi(
    fsl_rcsi_lessquality = "rCSILessQlty",
    fsl_rcsi_borrow = "rCSIBorrow",
    fsl_rcsi_mealsize = "rCSIMealSize",
    fsl_rcsi_mealadult = "rCSIMealAdult",
    fsl_rcsi_mealnb = "rCSIMealNb"
  ) %>%
  add_fcm_phase(
  )
```
:::

## Practice 2

- You receive a dataset, you need to review the following four indicators.

  - Food Consumption Score: **fsl_fcs_score**, **fsl_fcs_cat**
  - Household Hunger Score: **hhs_score**, **hhs_cat**
  
Don't forget to write the review.

```{r}
dataset_to_review <- read.csv("../inputs/06 - exercise - dataset_to_review.csv")

dataset_without_indicators <- addindicators::addindicators_MSNA_template_data
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the function `review_variables`
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

How was the FSC created?
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

How was coded the category for the HHS? 
Names in the dataset are: "hhs_cat", "hhs_score"
Names created with `add_hhs` are: "fsl_hhs_cat", "fsl_hhs_score"
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
my_review <- dataset_without_indicators %>% 
  add_fcs(
  cutoffs = "normal",
  fsl_fcs_cereal = "fs_fcs_cereals_grains_roots_tubers",
  fsl_fcs_legumes = "fs_fcs_beans_nuts",
  fsl_fcs_veg = "fs_fcs_vegetables_leaves",
  fsl_fcs_fruit = "fs_fcs_fruit",
  fsl_fcs_meat = "fs_fcs_meat_fish_eggs",
  fsl_fcs_dairy = "fs_fcs_dairy",
  fsl_fcs_sugar = "fs_fcs_sugar",
  fsl_fcs_oil = "fs_fcs_oil_fat_butter"
  ) %>%
  add_hhs(
  fsl_hhs_nofoodhh = "fs_hhs_nofood_yn",
  fsl_hhs_nofoodhh_freq = "fs_hhs_nofood_freq",
  fsl_hhs_sleephungry = "fs_hhs_sleephungry_yn",
  fsl_hhs_sleephungry_freq = "fs_hhs_sleephungry_freq",
  fsl_hhs_alldaynight = "fs_hhs_daynoteating_yn",
  fsl_hhs_alldaynight_freq = "fs_hhs_daynoteating_freq",
  yes_answer = "yes",
  no_answer = "no",
  rarely_answer = "rarely_1_2",
  sometimes_answer = "sometimes_3_10",
  often_answer = "often_10_times"
  ) %>% 
  select(uuid, fsl_fcs_cat, fsl_fcs_score, fsl_hhs_cat, fsl_hhs_score)
dataset_to_review <- full_join(dataset_to_review, my_review, by = "uuid")

review <- dataset_to_review %>% 
  review_variables(columns_to_review = c("fsl_fcs_cat.x", "fsl_fcs_score.x", "hhs_cat", "hhs_score"),
                   columns_to_compare_with = c("fsl_fcs_cat.y", "fsl_fcs_score.y", "fsl_hhs_cat", "fsl_hhs_score"))

review$review_table %>% 
  group_by(variable,review_check,review_comment) %>% 
  tally()
```

- There are 10 fcs categories that are different.
- There are 100 HHS categories that are different

```{r}
review$dataset %>% 
  filter(!review_check_fsl_fcs_cat.x) %>% 
  select(uuid, review_comment_fsl_fcs_cat.x, fsl_fcs_score.x, fsl_fcs_cat.x, fsl_fcs_cat.y)

```
- Food Consumption Score have different categories, what threshold were used to compute the FCS?  Maybe 28-42?


```{r}
review$dataset %>% 
  filter(!review_check_hhs_cat) %>% 
  select(hhs_cat, fsl_hhs_cat) %>% 
  table(useNA = "ifany")
```
- HHS is fine. Labeling is different
:::

## Downloads

[dataset_to_review](../inputs/06 - exercise - dataset_to_review.csv)
