---
title: "04 - Practice (2)"
date: last-modified

---

# Practice
```{r}
#| warning: false
library(cleaningtools)
library(dplyr)

my_raw_dataset <- cleaningtools::cleaningtools_raw_data
my_kobo_survey <- cleaningtools::cleaningtools_survey
my_kobo_choice <- cleaningtools::cleaningtools_choices
```

## Practice 1

- Export the cleaning log you have created previously. The previous log is loaded below.
```{r}
previous_exercise_log <- readRDS("../inputs/03 - exercise - previous_log.RDS")

previous_exercise_log %>% names()
```


::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint.

Did you try the function `create_combined_log`
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint.

Did you try the function `create_xlsx_cleaning_log`
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
previous_exercise_log %>% 
  create_combined_log() %>%
  create_xlsx_cleaning_log(output_path = "../outputs/03 - correction - cleaning_log.xlsx", 
                           kobo_survey = my_kobo_survey,
                           kobo_choices = my_kobo_choice,
                           sm_dropdown_type = "logical",
                           use_dropdown = TRUE)
  
```
:::

## Practice 2

- Create the clean data from the raw dataset and the filled cleaning.

```{r}
exercise_filled_log <- readxl::read_excel("../inputs/04 - exercise - cleaning_log - filled.xlsx", sheet = "cleaning_log")
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the function `create_clean_data`
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the function `recreate_parent_column`
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
exercise_clean_dataset <- create_clean_data(raw_dataset = my_raw_dataset,
                                            raw_data_uuid_column = "X_uuid",
                                            cleaning_log = exercise_filled_log, 
                                            cleaning_log_uuid_column = "uuid",
                                            cleaning_log_question_column = "question",
                                            cleaning_log_new_value_column = "new_value",
                                            cleaning_log_change_type_column = "change_type")


exercise_clean_dataset2 <- recreate_parent_column(exercise_clean_dataset,
                                                  uuid_column = "X_uuid", 
                                                  kobo_survey = my_kobo_survey,
                                                  kobo_choices = my_kobo_choice,
                                                  cleaning_log_to_append = exercise_filled_log)

  
```
:::

## Practice 3

- Review the cleaning below, if there is someone else doing the exercise, you can try to review someone's cleaning.

```{r}
exercise3_clean_dataset <- readxl::read_excel("../inputs/05 - exercise - clean dataset for review.xlsx")

exercise3_cleaning_log <- readxl::read_excel("../inputs/05 - exercise - clean dataset for review.xlsx", sheet = 2)

```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the function `review_cleaning`
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you separate the cleaning log?
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
exercise3_deletion_log <- exercise3_cleaning_log %>% 
  filter(change_type == "remove_survey")

exercise3_log_no_deletion <- exercise3_cleaning_log %>% 
  filter(change_type != "remove_survey") %>% 
  filter(!uuid %in% exercise3_deletion_log$uuid)

review_of_cleaning <- review_cleaning(raw_dataset = my_raw_dataset,
                                      raw_dataset_uuid_column = "X_uuid", 
                                      clean_dataset = exercise3_clean_dataset,
                                      clean_dataset_uuid_column = "X_uuid",
                                      cleaning_log = exercise3_log_no_deletion, 
                                      cleaning_log_uuid_column = "uuid",
                                      cleaning_log_question_column = "question",
                                      cleaning_log_new_value_column = "new_value",
                                      cleaning_log_change_type_column = "change_type", 
                                      cleaning_log_old_value_column = "old_value", 
                                      deletion_log = exercise3_deletion_log, 
                                      deletion_log_uuid_column = "uuid"
)
```

:::

## Downloads

- [03 - exercise - previous_log](../inputs/03 - exercise - previous_log.RDS)
- [03 - correction - cleaning_log.xlsx](../outputs/03 - correction - cleaning_log.xlsx)
- [04 - exercise - cleaning_log - filled.xlsx](../inputs/04 - exercise - cleaning_log - filled.xlsx)
- [05 - exercise - clean dataset for review](../inputs/05 - exercise - clean dataset for review.xlsx)
