---
title: "02 - Ratio"
author: "Yann Say"
date: last-modified

---
# Analysis - ratio

## `create_analysis_ratio`

```{r}
#| warning: false
#| output: false

library(analysistools)
library(dplyr)

my_data <- analysistools::analysistools_MSNA_template_data
set.seed(1323)
my_data <- my_data |>
  mutate(num_aged_school_children = round(runif(100, min = 0, max = 5)),
         num_enrolled_school_children = round(runif(100, min = 0, max = 5)),
         num_enrolled_school_children = case_when(num_aged_school_children == 0 ~ NA, num_aged_school_children < num_enrolled_school_children ~ num_aged_school_children,
                                                  TRUE ~ num_enrolled_school_children
                                                  ))
sampling_frame <- data.frame(
  strata = c("admin1a", "admin1b", "admin1c"),
  population = c(100000, 200000, 300000)
)

my_data <- my_data %>% 
  add_weights(sampling_frame, "admin1", "strata", "population")

my_design <- srvyr::as_survey_design(my_data, weights = "weights", strata = "admin1")
```

To calculate ratio, there are two functions `create_analysis_ratio` or `create_analysis` with a loa with more information. 

```{r}
my_loa_with_ratio <- read.csv("../inputs/07 - example - loa_with_ratio.csv")

```
```{r}
my_loa_with_ratio %>% 
  filter(analysis_type == "ratio") |>
  select(analysis_type, analysis_var, group_var, analysis_var_numerator, analysis_var_denominator)
```

```{r}
#| output: false
my_results_with_ratio <- create_analysis(my_design, loa = my_loa_with_ratio, sm_separator = "/")
```

```{r}
my_results_with_ratio$results_table %>% 
  filter(analysis_type == "ratio")
```

### Arguments of `create_analysis_ratio`

`create_analysis_ratio` has two arguments: `numerator_NA_to_0 ` and `filter_denominator_0 ` that by default are set to TRUE. 

- `numerator_NA_to_0` will turn all NA of the numerator into 0's, default TRUE.

- `filter_denominator_0` will remove all rows with 0's in the denominator, default TRUE.

The following example show a dataset with the number of children (*num_children*), the number of children enrolled to a school (*num_enrolled*) and the number of children attending school on a regular basis (*num_attending*).

```{r}
school_ex <- data.frame(
  hh = c("hh1", "hh2", "hh3", "hh4"),
  num_children = c(3, 0, 2, NA),
  num_enrolled = c(3, NA, 0, NA),
  num_attending = c(1, NA, NA, NA)
  )

me_design <- srvyr::as_survey(school_ex)

school_ex
```

- What is the ratio between children attending school and the number of children ?
- How many households are included in the calculation?

::: {.callout-tip collapse="true" appearance="minimal"}
###  Expand to get the answer

Default value will give a ratio of 0.2 as there are 1 child out of 5 attending school.

numerator: 1 child from hh1 and 0 from hh3. 

denominator: 3 from hh1 and 2 from hh3. In the hh3, the num_attending is NA because there is a skip logic, there cannot be a child attending as none are enrolled. 

By default, the function has the argument `numerator_NA_to_0` set to TRUE to turn that NA into a 0.

n and n_total are 2 as 2 households were included in the calculation. hh2 was not included in the calculation of totals. The argument `filter_denominator_0` set to TRUE removes that row.


``` {r}
create_analysis_ratio(me_design,
  analysis_var_numerator = "num_attending",
  analysis_var_denominator = "num_children") %>%
  select(analysis_type, analysis_var, stat, n, n_total, analysis_key)
```
:::

- What will be the ratio if only `numerator_NA_to_0` is set to FALSE ?
- How many households are included in the calculation?

::: {.callout-tip collapse="true" appearance="minimal"}
###  Expand to get the answer

Ratio will be 1/3, as hh3 with 2 children and NA for attending will be removed with the `na.rm = T` inside the `survey_ratio` calculation.

n and n_total is 1 as only 1 household was used.

``` {r}
create_analysis_ratio(me_design,
                      analysis_var_numerator = "num_attending",
                      analysis_var_denominator = "num_children",
                      numerator_NA_to_0 = FALSE) %>% 
  select(analysis_type, analysis_var, stat, n, n_total, analysis_key)
```
:::

- What will be the ratio if only `filter_denominator_0` is set to FALSE ?
- How many households are included in the calculation?

::: {.callout-tip collapse="true" appearance="minimal"}
###  Expand to get the answer

ratio will be 0.2 as there are 1 child out of 5 attending school.
The number of household counted, n and n_total, is equal to 3 instead 2. The household with 0 child is counted in the totals. (01 + 0 + 0) / (3 + 0 + 2)

```{r}
create_analysis_ratio(me_design,
                      analysis_var_numerator = "num_attending",
                      analysis_var_denominator = "num_children",
                      filter_denominator_0 = FALSE)  %>% 
  select(analysis_type, analysis_var, stat, n, n_total, analysis_key)
```

:::

## Downloads

- [07 - example - loa_with_ratio.csv](../inputs/07 - example - loa_with_ratio.csv)
