---
title: "02 - Practice (6)"
author: "Yann Say"
date: last-modified

---
# Practices

## Practice 1

- Review this analysis 

There is no weights. The strata are **admin1**
```{r}
#| message: false
library(analysistools)
library(dplyr)

analysis_to_review <- readxl::read_excel("../inputs/10 - exercise - analysis_to_review.xlsx")
dataset_to_review <- readxl::read_excel("../inputs/10 - exercise - analysis_to_review.xlsx", sheet = "dataset")
```

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
loa_for_review <- analysis_to_review %>% 
  create_loa_from_results()

review_design <- srvyr::as_survey_design(dataset_to_review, strata = "admin1")
my_analysis_exercise <- create_analysis(review_design, loa = loa_for_review, sm_separator = "/")

my_results_table_shorter <- my_analysis_exercise$results_table %>% 
  select(analysis_key, stat)

binded_results_table <- analysis_to_review %>% 
  full_join(my_results_table_shorter, by = "analysis_key")

exercise_review <- review_analysis(binded_results_table,
                                   stat_columns_to_review = "stat.x",
                                   stat_columns_to_compare_with = "stat.y", 
                                   analysis_key_column = "analysis_key")

exercise_review$review_table %>% 
  group_by(review_check,review_comment) %>% 
  tally()
```

:::

## Extra

How you would review an analysis that does not have an analysis key? (discussion)

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

- If the analysis is in long format, add the analysis key.
- If the analysis is in a wide format, change to long format then add the analysis key.

:::

## Downloads

- [10 - exercise - analysis_to_review](../inputs/10 - exercise - analysis_to_review.xlsx)
