---
title: "02 - Practice (4)"
date: last-modified

---
# Practice

## Practice 1

```{r}
library(analysistools)
library(dplyr)
```


```{r}
exercise_data <- analysistools_MSNA_template_data

only_nas <- exercise_data %>%
  summarise(across(.cols = everything(), .fns = function(x) {
    sum(is.na(x)) == nrow(exercise_data)
  })) %>%
  do.call(c, .)

exercise_data_shorter <- exercise_data[, !only_nas] %>%
  select(!grep("other", names(exercise_data), value = T))

exercise_data_shorter <- exercise_data_shorter[,1:30]
```


With the dataset *exercise_data*, please do the following:

- Create a results table at the level **respondent_gender**. Keep the strata at **admin1**

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the argument *group_var* in `create_analysis` ?
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| eval: false
my_exercise_design <- srvyr::as_survey_design(exercise_data_shorter, strata = "admin1") 

my_answer_analysis <- create_analysis(my_exercise_design, group_var = "respondent_gender", sm_separator = "/")

```
:::

## Practice 2

- The analysis should be weighted, this is the sampling frame. Re-do the analysis at the overall level.

```{r}
sampling_frame <- data.frame(
  strata = c("admin1a", "admin1b", "admin1c"),
  population = c(100000, 200000, 300000)
)
sampling_frame
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the function *add_weights* ?
:::

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you modify your design object?
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| eval: false

exercise_data_shorter_weigthed <- exercise_data_shorter %>% 
  add_weights(sample_data = sampling_frame, strata_column_dataset = "admin1", strata_column_sample = "strata", population_column = "population")

my_exercise_design_weigthed <- srvyr::as_survey_design(exercise_data_shorter_weigthed, strata = "admin1", weights = "weights") 

my_answer_analysis_weighted <- create_analysis(my_exercise_design_weigthed, sm_separator = "/")

```
:::
