---
title: "03 - Practice (7)"
date: last-modified
---

# Practice

## Practice 1

- Add labels to the following results table. 
```{r}
library(dplyr)
library(presentresults)
label_exercise_results <- readxl::read_excel("../inputs/11 - exercise - label.xlsx", sheet = "results_table")
label_exercise_kobo_survey <- readxl::read_excel("../inputs/11 - exercise - label.xlsx", sheet = "kobo_survey")
label_exercise_kobo_choices <- readxl::read_excel("../inputs/11 - exercise - label.xlsx", sheet = "kobo_choices")

```

```{r}
head(label_exercise_results)
```

```{r}
head(label_exercise_kobo_survey)
```

```{r}
head(label_exercise_kobo_choices)
```

::: {.callout-note collapse="true" appearance="minimal"}
### Expand to get a hint

Did you try the argument *label_column* in `review_kobo_labels` and `create_label_dictionary` ?
:::

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
review_kobo_labels_results <- review_kobo_labels(label_exercise_kobo_survey,
                                                 label_exercise_kobo_choices,
                                                 results_table = label_exercise_results, 
                                                 label_column = "label"
)

label_dictionary <- create_label_dictionary(label_exercise_kobo_survey, 
                                            label_exercise_kobo_choices, 
                                            results_table = label_exercise_results, 
                                            label_column = "label")

results_table_labeled <- add_label_columns_to_results_table(
  label_exercise_results,
  label_dictionary
)
  
```
:::

## Practice 2

- Create an excel table with the strata in the rows and the variables in the columns.

```{r}
#| message: false
library(presentresults)
library(dplyr)
```

```{r}
exercise_outputs <- readxl::read_excel("../inputs/10 - exercise - analysis_to_review.xlsx")

```

::: {.callout-tip collapse="true" appearance="minimal"}
### Expand to get the answer

```{r}
#| output: false
exercise_outputs %>% 
  create_table_group_x_variable() %>% 
  create_xlsx_group_x_variable(file_path = "../outputs/06 - correction - group_x_variable_table.xlsx", overwrite = T) 
  
```
:::

## Downloads

- [11 - exercise - analysis_to_review](../inputs/11 - exercise - label.xlsx)
- [10 - exercise - analysis_to_review](../inputs/10 - exercise - analysis_to_review.xlsx)
- [06 - correction - group_x_variable_table](../outputs/06 - correction - group_x_variable_table.xlsx)
