---
title: "01 - Labels"
author: "Yann Say"
date: last-modified
---

```{r}
#| message: false
library(presentresults)
library(dplyr)
# load dataset and kobo
results_table <- presentresults_MSNA2024_results_table

kobo_survey <- presentresults_MSNA2024_kobotool_template$kobo_survey
kobo_choices <- presentresults_MSNA2024_kobotool_template$kobo_choices
```
Most of the time, the information in a dataset will be using coding label, not very easy to read by a human. For example, in the following results table.

```{r}
results_table[c(1,9), c("analysis_var", "group_var", "group_var_value")]

```
With KOBO tool, the survey and choices sheets always always have at least one column label to show how the questions and choices should be read. It can be used to label the results table.
```{r}
kobo_survey |>
  tail() |>
  select(type, name, `label::english`)
```

```{r}
kobo_choices |>
  tail() |>
  select(list_name, name, `label::english`)
```

::: {.callout-note .column-margin}
If there are new variables added to the dataset, they should also be added in the KOBO tool.
:::

::: {.callout-note .column-margin}
If the labels should be changed to be better suited, you can add a new label column to the KOBO tool. It should be added to the survey and choice tab.
:::

Adding the labels to the results table will be done in three steps:

- reviewing the KOBO tool: to make sure there is no duplicated label (in particular in the question labels),
- creating the label dictionary: to reduce the KOBO tool to only the information needed,
- adding labels to the results table: to add columns with the label to the results table.

## Review KOBO tool

First the KOBO tool should be review to see if there is any duplicated label, names, etc. This will cause issues later one. In the following example, using `review_kobo_labels` with passing the results table will look at the variables names presents in the results, not all variables

::: {.callout-note .column-margin}
Current version looks for all choices, instead of just the one present in the table. It will be ammended later.
:::

```{r}
review_kobo_labels_results <- review_kobo_labels(kobo_survey,
  kobo_choices,
  results_table = results_table
)
review_kobo_labels_results
```

In this case we have the HHS frequency question repeated, to remove the duplication, I will add which one they are referring to.

```{r}
kobo_survey_fixed <- kobo_survey
kobo_survey_fixed[
  which(kobo_survey_fixed[["label::english"]] == "How often did this happen in the past [4 weeks/30 days]?"),
  "label::english"
] <- paste(
  "How often did this happen in the past [4 weeks/30 days]? ---",
  c(
    "In the past 4 weeks (30 days), was there ever no food to eat of any kind in your house because of lack of resources to get food?",
    "In the past 4 weeks (30 days), did you or any household member go to sleep at night hungry because there was not enough food?",
    "In the past 4 weeks (30 days), did you or any household member go a whole day or night without eating anything at all because there was not enough food?"
  )
)
```


In the choices sheet, there are 2 flags:

- Kobo choices sheet has duplicated names in the same list_name.	
- Kobo choices sheet has duplicated labels in the same list_name.	

For the duplicated names in the same list name, these were added with the composite indicators. I will just keep one.
```{r}
kobo_choices_fixed <- kobo_choices |>
  filter(!`label::english` %in% c(
    "No shelter (sleeping in the open)",
    "Surface water (river, dam, lake, pond, stream, canal, irrigation channel)"
  ))

duplicated_listname_label <- review_kobo_labels_results |> filter(comments == "Kobo choices sheet has duplicated labels in the same list_name.")
```

For the duplicated labels, these are because of the template. I will just add a number based on their order.
```{r}
kobo_choices_fixed <- kobo_choices_fixed |>
  group_by(list_name)  |> 
  mutate(`label::english` = case_when(
    list_name %in% duplicated_listname_label$list_name ~ paste(`label::english`, row_number()),
    TRUE ~ `label::english`
  ))  |> 
  ungroup()
```

I can review again.
```{r}
review_kobo_labels(kobo_survey_fixed, kobo_choices_fixed, results_table = results_table)
```

## Label dictionary

I can now create a dictionary that will be used to create labels.
```{r}
label_dictionary <- create_label_dictionary(kobo_survey_fixed, kobo_choices_fixed, results_table = results_table)

label_dictionary |>  names()
```
It will return a list with:

- dictionary_survey: the dictionary to be used for the names of variables
```{r}
label_dictionary$dictionary_survey |> head(10)
```
- dictionary_choices: the dictionary to be used for the value of the variables,



```{r}
label_dictionary$dictionary_choices |> head(10)

```
- analysis_type_dictionary: the dictionary to be used for the analysis_type column.

```{r}
label_dictionary$analysis_type_dictionary |> head(10)

```

::: {.callout-note .column-margin}
`analysis_type_dictionary` will always come in English, if you want to modify it please check the example of the function.
:::

## Add the label

Finally, using `add_label_columns_to_results_table` will add the label columns to the results table.
```{r}
results_table_labeled <- add_label_columns_to_results_table(
  results_table,
  label_dictionary
)

results_table_labeled [1,] |> 
  t()
```


This is section comes from this [vignette](https://impact-initiatives.github.io/presentresults/articles/add-label-to-results-table.html). 
